Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-10 paper/structureScene.tex
update section VI

For the ASS setting, evaluation is performed on the private dataset of the DCASE 2013 challenge. The metric used is the precision at rank $k$ ($p@k$), which is the  average  number  of  items  of  the  same  class among the $k$ closest items averaged for all possible seed items. The $p@k$ is computed for $k=[1,\ldots,9]$. Note that a $p@1$ is equivalent to an accuracy computed based on the labels of the 1st nearest neighbors of the items to classify.

For the ASC setting, the systems are evaluated  with five-fold  stratified cross validation on the private dataset of the DCASE 2013 challenge. The folds are identical to those used in the original challenge. Optimal parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approach and the scaling parameters $N$ of the RBF kernels (see Eq. \ref{eq:kc}), are learned on the public dataset of the DCASE 2013 challenge, using five-fold  stratified cross validation as well.

The \emph{ob} approach is compared to commonly used approaches using an early integration strategy (\emph{ei}) for the ASS setting, and both an early and a late integration (\emph{li}) strategy for the ASC setting (see Section \ref{sec:eili}).

@@

@@

As most of the 2013 DCASE challenge participants did, a Support Vector Machine (SVM), which is a large-margin binary discriminators with tunable regularization of misclassified examples, is used as classifier for the ASC setting. For the \emph{ob} approach, \gl{TODO}. For both the \emph{ei} and \emph{li} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approach, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All features, \emph{i.e.} the frames, the pooled frames or the centroids depending on the approach considered, are standardized prior to be filled into the classifier. The standardization is computed with respect to the train/test set split of the cross validation scheme (see Section \ref{sec:stand}).

>>>>

@@

For the ASS setting, evaluation is performed on the private dataset of the DCASE 2013 challenge. The metric used is the precision at rank $k$ ($p@k$), which is the  average  number  of  items  of  the  same  class among the $k$ closest items averaged for all possible seed items. The $p@k$ is computed for $k=[1,\ldots,9]$. Note that a $p@1$ is equivalent to an accuracy computed based on the labels of the 1st nearest neighbors of the items to classify. For each experimental setting, we report the results for the set of parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approach and the scaling parameters $N$ of the RBF kernels (see Eq. \ref{eq:kc}) giving the best $p@9$.

For the ASC setting, the systems are evaluated  with five-fold  stratified cross validation on the private dataset of the DCASE 2013 challenge. The folds are identical to those used in the original challenge. Optimal parameters (see above) are this time learned on the public dataset of the DCASE 2013 challenge, using five-fold  stratified cross validation as well.

The \emph{ob} approach is compared to commonly used approaches using an early integration strategy (\emph{ei}) for the ASS setting, and both an early and a late integration (\emph{li}) strategy for the ASC setting (see Section \ref{sec:eili}) \gl{TODO: maj vote}.

@@

As most of the 2013 DCASE challenge participants did, a Support Vector Machine (SVM), which is a large-margin binary discriminators with tunable regularization of misclassified examples, is used as classifier for the ASC setting. For the \emph{ob} approach, \gl{TODO: kernel used}. For both the \emph{ei} and \emph{li} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approach, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All features, \emph{i.e.} the frames, the pooled frames or the centroids depending on the approach considered, are standardized prior to be filled into the classifier. The standardization is computed with respect to the train/test set split of the cross validation scheme (see Section \ref{sec:stand}).
